Sampling Strategies in Decisions from Experience

### 2022-05-26 manuscript.Rmd
Add abstract

abstract: |
  Add abstract

keywords          : "risky choice, information sampling, evidence accumulation, computational modeling, cumulative prospect theory"
wordcount         : ""

@@

Relying on the sequential sampling framework, the decision-making processes were modeled as evidence accumulation over time. 
Two different models were presented ...

>>>>

abstract: |
  In the sampling paradigm, people can---as much as they want, in the way they want, and without costs---sample the possible outcomes of prospects before making a final choice. Do the sequential pattern in which the outcomes are sampled (sampling strategy) and the way the sampled outcomes are integrated and processed to evaluate the prospects (integration/decision strategy) act together to shape choices in the sampling paradigm? This paper presents two models that incorporate the potential interplay between both types of strategies into the sequential sampling framework. Each model assumes an evidence accumulation process representing a distinct integration/decision strategy, and allows for variations in the sampling strategy. In a computational analysis, both models are used to simulate choices between a safe and a risky prospect, while systematically varying sampling strategies and evidence thresholds. The simulations show that the potential interplay between sampling and integration/decision strategies can lead to systematically different choices patterns and can contribute to the as-if underweighting of rare outcomes pattern in decisions from experience, irrespective of the existence or absence of sampling error. The model-implied differences in the choice patterns translate to distinct signatures in cumulative prospect theory’s psychoeconomic value and weighting function.

keywords          : "decisions from experience, information sampling, evidence accumulation, computational modeling, cumulative prospect theory"
wordcount         : ""

@@

Relying on the sequential sampling framework, the decision-making processes were modeled as evidence accumulation over time. 
Two different models were presented
